\documentclass[a4paper,12pt]{article}
\usepackage{graphicx}
%%%% \usepackage{fancyhdr}
\usepackage{mathrsfs}
%\usepackage{psfig}
\usepackage{epsfig}
\usepackage{times}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[verbose]{geometry}
%\usepackage{rotating}
\usepackage{multirow}
\usepackage{color}
\usepackage{hyperref}
\usepackage[latin1]{inputenc}
\usepackage{verbatim}
\usepackage{natbib}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\rc}{\\[0.1 in]}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\geometry{top=2.5cm, bottom=4.5cm, left=2.5cm, right=2.5cm}
\setlength{\topskip}{1.0cm} \setlength{\headsep}{2.0cm}
\setlength{\footskip}{1.5cm}
\parskip=0pt
\parindent=0pt
%%%%\setlength{\textwidth}{16.5cm}
%%%%\setlength{\textheight}{23.0cm}
%%%%\setlength{\oddsidemargin}{-.40cm}

\renewcommand{\familydefault}{cmss}
\renewcommand{\seriesdefault}{m}
\DeclareSymbolFontAlphabet{\mathcal}{rsfs}
\bibliographystyle{elsart-harv}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\thispagestyle{empty}
%
\noindent Professor Neelesh A. Patankar, Assoc. Editor, JCP  

Northwestern University. 

Evanston, IL, USA$$$$


\hspace{6cm}Juan M. Gimenez.

\hspace{6cm}Centro de Investigaci\'on de M\'etodos Computacionales (CIMEC).

\hspace{6cm}Universidad Nacional del Litoral /CONICET.

\hspace{6cm}email: jmarcelogimenez@gmail.com

\hspace{6cm}http://www.cimec.org.ar

\hspace{6cm}

\hspace{6cm}Leo M. Gonz\'{a}lez

\hspace{6cm}Universidad Polit\'{e}cnica de Madrid (ETSIN-UPM)

\hspace{6cm}email: leo.gonzalez@upm.es

\hspace{6cm}http://www.cfm.upm.es/

\vspace{2cm}

$\quad$\hspace{10cm}Madrid, October. 08th, 2014
$$$$

\noindent Dear Sir:\rc
%
Please find enclosed for your kind review the manuscript entitled:
%
\begin{center}
``An extended validation of the last generation of particle finite element method for free surface flows''
\end{center}
%
In this paper, a new generation of the particle method known as Particle Finite
 Element Method (PFEM), which combines convective particle movement and a fixed 
 mesh resolution, is exhaustively tested on free surface flows. This interesting variant, 
 previously described in the literature as PFEM-2, is able to use larger time steps when compared to other similar numerical tools which implies shorter computational times while maintaining the accuracy of the computation. The main topic of this paper is the validation of the methodology for a wide wariety of problems. In order to achieve that, different improved versions of discontinuous and continuous enriched basis functions for the pressure field have been developed to obtain a general methodology, not restricted to a particular range of parameters.
%
% To our knowledge these topics have not been covered in other publications.
%
%
Thank you for your time and please report any mistake that we could be
committing in this submission.
%
We hope that the editorial committee will find the paper interesting and worth
publishing.

%
$$$$
Sincerely,
\vspace{0.5cm}

\ \ \ The Authors
$$\quad$$
%\bibliography{./../../../BIBTEX/bib}
% \bibliography{bib}
\end{document}
